When, why, and how to avoid, prefer, or tolerate inbreeding

### 2018-03-02 presentation/inbreeding.Rmd
Slide adjustments

![](images/male.png)

@@

More generally, is inclusive fitness from inbreeding (left) greater than inclusive fitness from outbreeding?

@@

<div align="left" style="line-height: 0.6em;">
<span style="font-size: 14px;">
[1] Parker (1979) *Sexual selection and reproductive competition in insects* (pp. 123–166). <br>
[2] Parker (2006) *Philos. Trans. Royal Soc. B.* [**361**:235-259](https://doi.org/10.1098/rstb.2005.1785). 
</span></div>

@@

- Does not consider complex strategies such as female multiple mating (polyandry) [but see 1]

@@

<div align="left" style="line-height: 0.6em;">
<span style="font-size: 14px;">
[1] Lehtonen, J & H Kokko (2015) *Proc. R. Soc. B* [**282**:20142716](http://rspb.royalsocietypublishing.org/content/282/1801/20142716).
</span></div>

@@

- Allows for simultaneous evolution of inbreeding behaviour and polyandry

- Allows for the evolution of pre- and post-copulatory inbreeding behaviour

>>>>

**Predict when inbreeding avoidance, preference, and tolerance will occur in obligately biparental diploid populations**

@@

More generally, is inclusive fitness from inbreeding (right) greater than inclusive fitness from outbreeding (left)?

@@

<div align="left" style="line-height: 0.6em;">
<span style="font-size: 14px;">
[1] Parker (1979) *Sexual selection and reproductive competition in insects* (pp. 123–166).
[2] Parker (2006) *Philos. Trans. Royal Soc. B.* [**361**:235-259](https://doi.org/10.1098/rstb.2005.1785). 
</span></div>

- **Above** thresholds we predict inbreeding avoidance

- **Below** thresholds we predict inbreeding preference (females) or tolerance (males) [3,4]

<div align="left" style="line-height: 0.6em;">
<span style="font-size: 14px;">
[1] Parker (1979) *Sexual selection and reproductive competition in insects* (pp. 123–166). 
[2] Parker (2006) *Philos. Trans. Royal Soc. B.* [**361**:235-259](https://doi.org/10.1098/rstb.2005.1785). <br>
[3] Puurtinen (2011) *Evolution* [**65**:1501-1505](https://doi.org/10.1111/j.1558-5646.2010.01217.x).
[4] Duthie, AB & JM Reid (2016) *Am. Nat.* [188:651-667](https://bradduthie.github.io/Duthie_Reid2016.pdf).

</span></div>

@@

- Does not consider complex genetic architecture

@@

@@

- Account for complex genetic architecture undelrying phenotypes

- Allows for the evolution of pre- and post-copulatory inbreeding, and polyandry
